---
title: "HLM Analysis for Udio"
author: "Paul Xu"
date: "October 7, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Process and get data from common.R
source("common.R")
library(stargazer)
UDIO_DATASET_C <- UDIO_DATASET_C[UDIO_CONDITION != "Supported",]
```

## Description of the model-building process

Tables 1-4 describe the HLM models with student performance on posttests of RAPID Reading Comprehension, WIAT Standardized Scores, Reading MRQ, and QRI respectively as outcome variables.  The model building process follows this procedure: Model 1 is the unconditional model.  Model 2 adds student demographic information, such as ELL status, IEP status, and Free/Reduced Lunch status, to the unconditional model.  In model 3, student performance on the pretests are added as control variables, and RAPID subscores are added as predictors as well.  Model 4 is based on model 3, with non-significant RAPID subscores removed, and with Udio Condition added as main effects.  Model 5 further extends model 4 with additional predictors, such as MRQ, WIAT, wherever such addition is seen fit.  All models has only intercept as random effect - all models are random-intercept models.  To build random-slope models, all variables need to be normalized for models to converge, which will make parameter estimates look drastically different from random-intercept models, so random-slope models are not attempted for now.  Please see next page for the regression tables.  Varance components of all random effects are listed.

```{r rapid_rc, include=FALSE, echo=FALSE}
rc.model.1 <- lmer(POST_RAPID_RC_AB ~ (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.2 <- lmer(POST_RAPID_RC_AB ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.3 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.4 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.5 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + 
                     POST_R_MRQ_C + POST_QRI_C + (1|CLASS_ID), data = UDIO_DATASET_C)
# rc.model.4 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
#                      POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + UDIO_CONDITION + (1+PRE_RAPID_RC_AB_C|CLASS_ID), 
#                    data = UDIO_DATASET_C)
# rc.model.5 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
#                      POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + UDIO_CONDITION + PRE_RAPID_RC_AB:UDIO_CONDITION + (1+PRE_RAPID_RC_AB_C|CLASS_ID), 
#                    data = UDIO_DATASET_C)
```

```{r rapid_rc.table, results="asis", echo=FALSE}
rc <- list(rc.model.1, rc.model.2, rc.model.3, rc.model.4, rc.model.5)
stargazer(rc, title = "HLM Results for RAPID Reading Comprehension Scores",
          dep.var.labels = "Reading Comp. (Post)",
          covariate.labels = c("Intercept", "Reading Comp. (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Full", "Supported", "WIAT SS (Post)", "Reading MRQ (Post)"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(rc), notes = "All predictors are grand-mean centered", notes.append = TRUE,
          table.placement = "h")
```

```{r wiat, echo=FALSE}
wiat.model.1 <- lmer(POST_WIAT_SS ~ (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.2 <- lmer(POST_WIAT_SS ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.3 <- lmer(POST_WIAT_SS ~ ELL + IEP + FARMS + PRE_WIAT_SS_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + 
                       POST_RAPID_SK_AB_C + POST_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.4 <- lmer(POST_WIAT_SS ~ ELL + IEP + FARMS + PRE_WIAT_SS_C + POST_RAPID_VK_AB_C + 
                       POST_RAPID_RC_AB_C + POST_QRI_PCT + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.5 <- lmer(POST_WIAT_SS ~ ELL + IEP + FARMS + PRE_WIAT_SS_C + POST_RAPID_VK_AB_C + 
                       POST_RAPID_RC_AB_C + POST_W_MRQ + POST_QRI_PCT + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r wiat_table, results="asis", echo=FALSE}
wiat <- list(wiat.model.1, wiat.model.2, wiat.model.3, wiat.model.4, wiat.model.5)
stargazer(wiat, title = "HLM Results for WIAT Standardized Scores",
          dep.var.labels = "WIAT Standardized Score (Post)",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "WIAT SS (Pre)", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "Full", "Supported", "Reading MRQ (Post)"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(wiat), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

```{r mrq, echo = FALSE}
mrq.model.1 <- lmer(POST_R_MRQ ~ (1|CLASS_ID), data = UDIO_DATASET_C)
mrq.model.2 <- lmer(POST_R_MRQ ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
mrq.model.3 <- lmer(POST_R_MRQ ~ ELL + IEP + FARMS + PRE_R_MRQ_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + + POST_RAPID_SK_AB_C + POST_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
mrq.model.4 <- lmer(POST_R_MRQ ~ ELL + IEP + FARMS + PRE_R_MRQ_C + UDIO_CONDITION + (1|CLASS_ID), data = UDIO_DATASET_C)
mrq.model.5 <- lmer(POST_R_MRQ ~ ELL + IEP + FARMS + PRE_R_MRQ_C + UDIO_CONDITION + POST_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r mrq_table, results="asis", echo=FALSE}
mrq <- list(mrq.model.1, mrq.model.2, mrq.model.3, mrq.model.4, mrq.model.5)
stargazer(mrq, title = "HLM models for MRQ (Post)",
          dep.var.labels = "Average Score for MRQ (Post)",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Reading MRQ (Pre)", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "Full", "Supported", "WIAT SS (Post)"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(mrq), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

```{r qri, echo = FALSE}
qri.model.1 <- lmer(POST_QRI_PCT ~ (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.2 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.3 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.4 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + UDIO_CONDITION + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.5 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  UDIO_CONDITION + POST_WIAT_SS_C + POST_R_MRQ_C + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r qri_table, results="asis", echo=FALSE}
qri <- list(qri.model.1, qri.model.2, qri.model.3, qri.model.4, qri.model.5)
stargazer(qri, title = "HLM models for QRI Percentatge Score (Post)",
          dep.var.labels = "Percentage Score for QRI (Post)",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "QRI (Pre)", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Full", "Supported", "WIAT SS (Post)", "Reading MRQ (Post)"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(qri), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```