---
title: "Udio HLM Results"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Process and get data from common.R
source("common.R")
library(stargazer)
UDIO_DATASET_C <- UDIO_DATASET_C[UDIO_DATASET_C$UDIO_CONDITION != "Supported",]
UDIO_DATASET_C$DIFF_RC <- UDIO_DATASET_C$POST_RAPID_RC_AB - UDIO_DATASET_C$PRE_RAPID_RC_AB
UDIO_DATASET_C$DIFF_WIAT <- UDIO_DATASET_C$POST_WIAT_SS - UDIO_DATASET_C$PRE_WIAT_SS
UDIO_DATASET_C$DIFF_QRI <- UDIO_DATASET_C$POST_QRI_PCT - UDIO_DATASET_C$PRE_QRI_PCT
UDIO_DATASET_C$DIFF_WR <- UDIO_DATASET_C$POST_RAPID_WR_AB - UDIO_DATASET_C$PRE_RAPID_WR_AB
UDIO_DATASET_C$DIFF_SK <- UDIO_DATASET_C$POST_RAPID_SK_AB - UDIO_DATASET_C$PRE_RAPID_SK_AB
UDIO_DATASET_C$DIFF_VK <- UDIO_DATASET_C$POST_RAPID_VK_AB - UDIO_DATASET_C$PRE_RAPID_VK_AB
UDIO_DATASET_C$DIFF_MRQ <- UDIO_DATASET_C$POST_R_MRQ - UDIO_DATASET_C$PRE_R_MRQ
UDIO_DATASET_F <- UDIO_DATASET_C[UDIO_DATASET_C$UDIO_CONDITION == "Full",]
```

#### Part 1. HLM Models based on RAPID Reading Comprehension
##### Table 1. Predicting post outcome with post outcomes (all students)

```{r rapid_rc, include=FALSE, echo=FALSE}
rc.model.1 <- lmer(POST_RAPID_RC_AB ~ (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.2 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.3 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.4 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.5 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C +
                     (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.6 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:IEP +
                     (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.7 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:ELL +
                     (1|CLASS_ID), data = UDIO_DATASET_C)
rc.model.8 <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:FARMS +
                     (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r rapid_rc.table, results="asis", echo=FALSE}
rc <- list(rc.model.1, rc.model.2, rc.model.3, rc.model.4, rc.model.5, rc.model.6)
stargazer(rc, title = "HLM Results for RAPID Reading Comprehension Scores",
          dep.var.labels = "Reading Comp. (Post)",
          covariate.labels = c("Intercept", "Reading Comp. (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "WIAT SS (Post)", "TTS Use (Log)", "TTS x IEP"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(rc, length(rc)), notes = "All predictors are grand-mean centered", notes.append = TRUE,
          table.placement = "h!")
```

##### Table 2. Predicting post outcome with post outcomes (full condition only)

```{r rapid_rc_f, include=FALSE, echo=FALSE}
rc.model.1f <- lmer(POST_RAPID_RC_AB ~ (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.2f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.3f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.4f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.5f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C + 
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C +
                     (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.6f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:IEP +
                     (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.7f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:ELL +
                     (1|CLASS_ID), data = UDIO_DATASET_F)
rc.model.8f <- lmer(POST_RAPID_RC_AB ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + POST_RAPID_WR_AB_C +
                     POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:FARMS +
                     (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r rapid_rc_f.table, results="asis", echo=FALSE}
rc.f <- list(rc.model.3f, rc.model.4f, rc.model.5f, rc.model.6f, rc.model.7f, rc.model.8f)
stargazer(rc.f, title = "HLM Results for RAPID Reading Comprehension Scores (Full Condition)",
          dep.var.labels = "Reading Comp. (Post)",
          covariate.labels = c("Intercept", "Reading Comp. (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "WIAT SS (Post)", "TTS Use (log)", "TTS x IEP", "TTS x ELL", "TTS x FARMS"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(rc.f, length(rc.f)), notes = "All predictors are grand-mean centered", notes.append = TRUE,
          table.placement = "h!")
```

##### Table 3. Predicting difference scores with pre outcomes (all students)

```{r rapid_diff_rc, include=FALSE, echo=FALSE}
rc.diff.1 <- lmer(DIFF_RC ~ (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.2 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.3 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.4 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.5 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + PRE_R_MRQ + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.6 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.7 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
rc.diff.8 <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r rapid_diff_rc.table, results="asis", echo=FALSE}
rc.diff <- list(rc.diff.3, rc.diff.4, rc.diff.5, rc.diff.6, rc.diff.7, rc.diff.8)
stargazer(rc.diff, title = "HLM Results for RAPID Reading Comprehension Difference Scores",
          dep.var.labels = "Reading Comp. Diff. Score",
          covariate.labels = c("Intercept", "Reading Comp. (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "WIAT SS (Pre)", "Read MRQ (Pre)", "TTS (log)", "TTS x IEP", "TTS x ELL", "TTS x FARMS"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(rc.diff, length(rc.diff)), notes = "All predictors are grand-mean centered", notes.append = TRUE,
          table.placement = "h!")
```

##### Table 4. Predicting difference scores with pre outcomes (full condition only)

```{r rapid_diff_rc_f, include=FALSE, echo=FALSE}
rc.diff.1f <- lmer(DIFF_RC ~ (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.2f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.3f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.4f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.5f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + PRE_R_MRQ + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.6f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.7f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
rc.diff.8f <- lmer(DIFF_RC ~ PRE_RAPID_RC_AB_C + ELL + IEP + FARMS + PRE_RAPID_WR_AB_C + 
                     PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_WIAT_SS_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r rapid_diff_rc_f.table, results="asis", echo=FALSE}
rc.diff.f <- list(rc.diff.3f, rc.diff.4f, rc.diff.5f, rc.diff.6f, rc.diff.7f, rc.diff.8f)
stargazer(rc.diff.f, title = "HLM Results for RAPID Reading Comprehension Difference Scores (Full condition only)",
          dep.var.labels = "Reading Comp. Diff. Score",
          covariate.labels = c("Intercept", "Reading Comp. (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "WIAT SS (Pre)", "Read MRQ (Pre)", "TTS (log)", "TTS x IEP", "TTS x ELL", "TTS x FARMS"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(rc.diff.f, length(rc.diff.f)), notes = "All predictors are grand-mean centered", notes.append = TRUE,
          table.placement = "h!")
```

#### Part 2 Models based on WIAT (Writing)
##### Table 5. Predicting post outcome with post outcomes (all students)

```{r wiat, echo=FALSE, include=FALSE}
wiat.model.1 <- lmer(POST_WIAT_SS ~ (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.2 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.3 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.4 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.5 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.6 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.7 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.model.8 <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r wiat_table, results="asis", echo=FALSE}
wiat <- list(wiat.model.1, wiat.model.2, wiat.model.3, wiat.model.4, wiat.model.5, wiat.model.6)
stargazer(wiat, title = "HLM Results for WIAT Standardized Scores",
          dep.var.labels = "WIAT Standardized Score (Post)",
          covariate.labels = c("Intercept", "WIAT SS (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Keyboarding", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "TTS Usage (log)", "TTS:IEP"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(wiat, length(wiat)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 6. Predicting post outcome with post outcomes (full condition only)

```{r wiat.f, echo=FALSE, include=FALSE}
wiat.model.1f <- lmer(POST_WIAT_SS ~ (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.2f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.3f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.4f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.5f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.6f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.7f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.model.8f <- lmer(POST_WIAT_SS ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r wiat_table.f, results="asis", echo=FALSE}
wiat.f <- list(wiat.model.1f, wiat.model.2f, wiat.model.3f, wiat.model.4f, wiat.model.5f, wiat.model.6f)
stargazer(wiat.f, title = "HLM Results for WIAT Standardized Scores (Full Condition Only)",
          dep.var.labels = "WIAT Standardized Score (Post)",
          covariate.labels = c("Intercept", "WIAT SS (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Keyboarding", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "TTS Usage (log)", "TTS:IEP"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(wiat.f, length(wiat.f)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 7. Predicting difference scores with pre outcomes (all students)

```{r wiat.diff, echo=FALSE}
wiat.diff.1 <- lmer(DIFF_WIAT ~ (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.2 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.3 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.4 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.5 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_RAPID_RC_AB_C + PRE_W_MRQ_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.6 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.7 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.8 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)

wiat.diff.9 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.10 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.11 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)

wiat.diff.12 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.13 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
wiat.diff.14 <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r wiat_table.diff, results="asis", echo=FALSE}
wiat.diff <- list(wiat.diff.1, wiat.diff.2, wiat.diff.3, wiat.diff.4, wiat.diff.5, wiat.diff.6)
stargazer(wiat.diff, title = "HLM Results for WIAT Difference Scores",
          dep.var.labels = "WIAT Difference Score",
          covariate.labels = c("Intercept", "WIAT SS (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Keyboarding", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "Reading Comp. (Pre)", "Writing MRQ (Pre)", "TTS Usage (log)", "TTS x IEP"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(wiat.diff, length(wiat.diff)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 8. Predicting difference scores with pre outcomes (full condition only)

```{r wiat.diff.f, echo=FALSE}
wiat.diff.1f <- lmer(DIFF_WIAT ~ (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.2f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.3f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.4f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.5f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_RAPID_RC_AB_C + PRE_W_MRQ_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.6f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.7f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.8f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)

wiat.diff.9f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.10f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.11f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_W_MRQ_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)

wiat.diff.12f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.13f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
wiat.diff.14f <- lmer(DIFF_WIAT ~ PRE_WIAT_SS_C + ELL + IEP + FARMS + KEY_MATCH_C + PRE_W_MRQ_C + PRE_WIAT_SS_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r wiat_table.diff.f, results="asis", echo=FALSE}
wiat.diff.f <- list(wiat.diff.1f, wiat.diff.2f, wiat.diff.3f, wiat.diff.4f, wiat.diff.5f, wiat.diff.6f)
stargazer(wiat.diff.f, title = "HLM Results for Difference Scores (Full Condition Only)",
          dep.var.labels = "WIAT Difference Score",
          covariate.labels = c("Intercept", "WIAT SS (Pre)", "ELL Status", "IEP Status", "Free/Reduced Lunch", "Keyboarding", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "Reading Comp. (Pre)", "Writing MRQ (Pre)", "TTS Usage (log)", "TTS x IEP"),
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(wiat.diff, length(wiat.diff)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

#### Part 3. Models based on QRI
##### Table 9. Predicting post outcome with post outcomes (all students)

```{r qri, echo = FALSE, include = FALSE}
qri.model.1 <- lmer(POST_QRI_PCT ~ (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.2 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.3 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.4 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + POST_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.5 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_C)

qri.model.6 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.7 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.model.8 <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r qri_table, results="asis", echo=FALSE}
qri <- list(qri.model.1, qri.model.2, qri.model.3, qri.model.4, qri.model.5, qri.model.6)
stargazer(qri, title = "HLM models for QRI Percentatge Score (Post)",
          dep.var.labels = "Percentage Score for QRI (Post)",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "QRI (Pre)", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "WIAT SS (Post)", "Keyboarding", "TTS Usage (log)", "TTS x ELL"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(qri), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 10. Predicting post outcome with post outcomes (full condition only)

```{r qri.f, echo = FALSE, include = FALSE}
qri.model.1f <- lmer(POST_QRI_PCT ~ (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.2f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.3f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_SK_AB_C + POST_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.4f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C + POST_RAPID_RC_AB_C + POST_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.5f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_F)

qri.model.6f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.7f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.model.8f <- lmer(POST_QRI_PCT ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + POST_RAPID_WR_AB_C + POST_RAPID_VK_AB_C +  POST_RAPID_RC_AB_C + POST_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r qri_table.f, results="asis", echo=FALSE}
qri.f <- list(qri.model.1f, qri.model.2f, qri.model.3f, qri.model.4f, qri.model.5f, qri.model.6f)
stargazer(qri, title = "HLM models for QRI Percentatge Score (Full Condition Only)",
          dep.var.labels = "Percentage Score for QRI (Post)",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "QRI (Pre)", "Word Recog. (Post)", "Voc. Know. (Post)", "Syn. Know. (Post)", "Reading Comp. (Post)", "WIAT SS (Post)", "Keyboarding", "TTS Usage (log)", "TTS x ELL"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(qri.f, length(qri.f)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 11. Predicting difference scores with pre outcomes (all students)

```{r qri.diff, echo = FALSE, include = FALSE}
qri.diff.1 <- lmer(DIFF_QRI ~ (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.2 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.3 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.4 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.5 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.6 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.7 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_C)
qri.diff.8 <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_C)
```

```{r qri_table.diff, results="asis", echo=FALSE}
qri.diff <- list(qri.diff.1, qri.diff.2, qri.diff.3, qri.diff.4, qri.diff.5, qri.diff.6)
stargazer(qri.diff, title = "HLM models for QRI Difference Scores",
          dep.var.labels = "Difference Score for QRI",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "QRI (Pre)", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "Reading Comp. (Pre)", "WIAT SS (Post)", "Keyboarding", "TTS Usage (log)", "TTS x IEP"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(qri.diff, length(qri.diff)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```

##### Table 12. Predicting difference scores with pre outcomes (full condition only)

```{r qri.diff.f, echo = FALSE, include = FALSE}
qri.diff.1f <- lmer(DIFF_QRI ~ (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.2f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.3f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_SK_AB_C + PRE_RAPID_RC_AB_C + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.4f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C + PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.5f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.6f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:IEP + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.7f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:ELL + (1|CLASS_ID), data = UDIO_DATASET_F)
qri.diff.8f <- lmer(DIFF_QRI ~ ELL + IEP + FARMS + PRE_QRI_PCT_C + PRE_RAPID_WR_AB_C + PRE_RAPID_VK_AB_C +  PRE_RAPID_RC_AB_C + PRE_WIAT_SS_C + KEY_MATCH_C + TTS_LOG_C + TTS_LOG_C:FARMS + (1|CLASS_ID), data = UDIO_DATASET_F)
```

```{r qri_table.diff.f, results="asis", echo=FALSE}
qri.diff.f <- list(qri.diff.1f, qri.diff.2f, qri.diff.3f, qri.diff.4f, qri.diff.5f, qri.diff.6f)
stargazer(qri.diff.f, title = "HLM models for QRI Difference Scores (Full Condition Only)",
          dep.var.labels = "Difference Score for QRI",
          covariate.labels = c("Intercept", "ELL Status", "IEP Status", "Free/Reduced Lunch", "QRI (Pre)", "Word Recog. (Pre)", "Voc. Know. (Pre)", "Syn. Know. (Pre)", "Reading Comp. (Pre)", "WIAT SS (Post)", "Keyboarding", "TTS Usage (log)", "TTS x IEP"), 
          header = F, type = "latex", intercept.bottom = FALSE,
          add.lines = varComp(qri.diff.f, length(qri.diff.f)), notes = "All predictors are grand-mean centered", notes.append = TRUE)
```